HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-06 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex

We would like to thank the reviewer for the appreciation of the paper and the constructive feedback. We have carefully considered all comments and we will propose a revision of the paper accordingly. In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.

\section*{Detailed responses}

\subsection*{Requested changes:}
\begin{itemize}
	\item {\em ``The reliability of the data is important for the use of this data by third parties. Please explain in detail how the human processing was done. Also, to what extent can machine failures be included in image processing ? Do humans correct them ?''} \medskip

	\textbf{Author response:} We thank the referee for this remark. Regarding the data-acquisition pipeline presented in Section 2, the human actions are limited. The only human processing comes at the step where the fashion trends are defined. The features are automatically detected by the vision recognition models. Then, we only define trends that are relevant for the fashion industry. For instance, the Mini A-line dress fashion trend is identified where the dress category is detected with a particular shape and a particular length, all of these details detected with different models. These associations of fine-grain attributes are defined by a team of fashion experts and are not provided with the paper. 
Concerning the machine failures, all the visual recognition models used to build the proposed dataset have been trained with a standard process involving a train, a eval and a test set. Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed. Please note that the data acquisition pipeline has been detailed and extended in Section 2. \\

@@

	\item {\em ``In publishing the data, it would be good to add a little more analysis of the characteristics of the data. For example, basic statistics for each market, statistics for the Weak signal $w^{f,i}_t$, etc.''} \medskip

	\textbf{Author response:} We agree with the referee and we acknowledge that we have not sufficiently presented the diversity of behaviours hidden in the proposed fashion dataset. So as to improve this point, a new section is added in appendix of the revised version of the paper where 4 different sub-samples of time series are defined and studied separately. \\

	\item {\em ``It is written that represents the index of fashion trends, but it is unclear what exactly it refers to. Does it correspond to a product/item?''} \medskip

	\textbf{Author response:} We understand this remark and further information has been added in the revised paper to clarify this point. The index of fashion trends represents the name of a fashion clothing relevant for the fashion industry. It can be just one attribute detected by a visual recognition model (ex: the Sneakers) but it can also be a combination of several attributes (ex: the Slim Sole Retro Basketball Sneakers). As the fashion trends names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\

### 2023-07-06 tmlr_submission/hermes_paper_revision/hermes_paper.tex
updates of Jean on the main paper + answer reviewer 3

At inference time, we first apply the localisation model which predicts boxes of generic fashion items (tops, pants, shoes, dresses, etc.) for each image. Then, each fashion item is cropped from its full image, resized to the classifiers' input size ($299\times299\,$px) and fed into the related classifier: a top will be fed into the model trained on tops, etc. We obtain for each image a set of boxes, associated with a general category and a set of fine-grain attributes describing this object. As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry. \textcolor{orange}{We call them fashion trends. They can be just one attribute detected by a visual recognition model, for example the sneakers fashion trend. They can also be a combination of several attributes, for instance the A-line dress fashion trend which is a combination of several attributes (dress length, collar shape, etc..) each one detected with a specific vision recognition model.}

@@

With this paper, we provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets. Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends. A central point of this work is to accurately detect and forecast such trends. In addition, each fashion time series is linked with its associated normalized fashion forward signal as presented in the section above. An overview of the dataset can be found in Table~\ref{tab:fashiondataset}. \textcolor{orange}{For privacy issues, all the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.}

>>>>

At inference time, we first apply the localisation model which predicts boxes of generic fashion items (tops, pants, shoes, dresses, etc.) for each image. Then, each fashion item is cropped from its full image, resized to the classifiers' input size ($299\times299\,$px) and fed into the related classifier: a top will be fed into the model trained on tops, etc. We obtain for each image a set of boxes, associated with a general category and a set of fine-grain attributes describing this object. As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry. \textcolor{orange}{We call them fashion trends. They can be just one attribute detected by a visual recognition model, for example the sneakers fashion trend. They can also be a combination of several attributes, for instance the Mini A-line dress fashion trend which is a combination of several attributes (dress length, shape, category,...) each one detected with a specific vision recognition model.}

@@

With this paper, we provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets. Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends. A central point of this work is to accurately detect and forecast such trends. In addition, each fashion time series is linked with its associated normalized fashion forward signal as presented in the section above. An overview of the dataset can be found in Table~\ref{tab:fashiondataset}. \textcolor{orange}{All the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.}
